---
title: "Practical Machine Learning Assessment"
author: "£ukasz Grzybowski"
output: html_document
---
### 1.Introduction
The goal of project is to predict the manner in which people did the exercise based on provided data.
For more information please go to http://groupware.les.inf.puc-rio.br/har.

### 2.Read data
Data come from:

- training data: https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv
- testing data: https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv
```{r,cache=TRUE}
train<-read.csv("./data/pml-training.csv")
test<-read.csv("./data/pml-testing.csv")
```

### 3.Feature selection
Dataset has 160 variables. It is necessary to select most important of them. Variables like `user_name`, `cvtd_timestamp` and `x` are to unique and not useful. Part of them have a lot of missing values. Another have near to zero variance. None of them are useful for prediction model.
```{r,warning=FALSE,message=FALSE}
set.seed(10)
library(caret)

# check variance
nz<-nearZeroVar(train)
# remove near zero varianve variables
ftrain<-train[,-nz]
# remove x,user_name,cvtd_timestamp variables
ftrain<-ftrain[,-c(1,2,5)]
# remain variables without missing values
missing<-sapply(ftrain, function(x) sum(is.na(x)))
nonZeroVars<-names(missing[missing==0])
ftrain<-ftrain[,nonZeroVars]
cor<-cor(ftrain[,-56])
cor<-findCorrelation(cor,cutoff=0.8)
ftrain<-ftrain[,-cor]
```

### 4.Prediction model
Used Random Forest predictive model based on 44 variables. Train set is divided into training (70%) and testing set (30%).
```{r,warning=FALSE,message=FALSE,cache=TRUE}
library(randomForest)

inTrain<-createDataPartition(y=ftrain$classe,p=0.7,list=FALSE)
training<-ftrain[inTrain,]
testing<-ftrain[-inTrain,]

model<-train(classe~.,method="rf",data=training,ntree=10)
model
```
### 5.Result
In sampe and out sample accuracy are similar about 99% (1% is error). Random forest algorithm give very good model.
```{r,warning=FALSE,message=FALSE,cache=TRUE}
pred<-predict(model,testing)
confusionMatrix(pred, testing$classe)
```
### 6.Prediction
Finally prediction is:
```{r,warning=FALSE,message=FALSE,cache=TRUE}
final<-predict(model,test)
final
```